---
title: "Making Interactive Plots"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Plotly

I am going to be making interactive plots using `Plotly` using the NYC DOHMH data on [NYC Restaurant Inspections](https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j/about_data).

```{r, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```


### Making Bar Graphs

Initial data cleaning, filtering, and making bar graphs:

```{r}
data("rest_inspec")

rest_inspec |> 
  filter(
    grade %in% c("A", "B", "C"), boro != "Missing",
    str_detect(dba, "[Cc][Oo][Ff][Ff][Ee][Ee]")) |> 
  group_by(boro, grade) |> 
  count(boro) |> 
  mutate(
    boro = str_to_title(boro),
    boro = fct_reorder(boro, n)) |> 
  plot_ly(
    x = ~boro, y = ~n, type = "bar", color = ~grade) |> 
  layout(barmode = "stack")
```

Notable Steps:

* I am removing inspections with scores other than `A`, `B`, or `C`, and remove entries with missing borough information. 
* I am filtering based on just `coffee shops` and examining grades based on borough. 
* Visualize data by first making a bar graph showing the **total number of coffee shops based on borough**. You can hover over each bar to see the number of coffee shops with `A`, `B`, or `C` grades in that borough.


This next bar graph will show the **top 10 most common critical violations for coffee shops by borough**:

```{r}
rest_inspec |> 
  filter(
    critical_flag == "Critical",
    grade %in% c("A", "B", "C"), boro != "Missing",
    str_detect(dba, "[Cc][Oo][Ff][Ff][Ee][Ee]")) |> 
  group_by(boro, violation_code, violation_description) |> 
  summarize(n = n(), .groups = "drop") |> 
  group_by(boro) |> 
  slice_max(n, n = 5) |> 
  mutate(text_label = str_c("Violation: ", violation_description)) |> 
  plot_ly(x = ~reorder(violation_code, n), y = ~n, type = "bar", color = ~boro, 
    text = ~text_label) |> 
  layout(
    xaxis = list(title = "Violation Code"),
    yaxis = list(title = "Count"),
    barmode = "stack")
```

Notable Steps:

* I filtered based on inspections with a `critical` flag, scores only with `A`, `B`, or `C`, entries with borough information, coffee shops, 
* **NOTE**: you can hover over each bar to see the violation description.


### Making a Line Plot

```{r}
rest_inspec |> 
  filter(critical_flag == "Critical",
         grade %in% c("A", "B", "C"), boro != "Missing",
         grade_date >= as.Date("2015-01-01"), 
         grade_date <= as.Date("2015-12-31")) |> 
  count(boro, grade_date) |> 
  plot_ly(
    x = ~grade_date, y = ~n, type = "scatter", mode = "lines", color = ~boro)
```


This figure shows the **trend of critical violations for all restaurants across all boroughs in 2015**. 

Notable steps:

* I only included inspections that had a critical flag, in the year of 2015, those that had a grade A, B, or C, and had a borough identified. 
* **Note**: You can hover over the line to see the number of critical violations for the specific date.